Prefetching SPARQL query cacher

### 2016-07-28 dissertation/cache-proxy.tex
Note IDP

@@

Based on the algebra tree and plans generated by the models or the
default query planner, as well as the access plans, several
alternative plans will be generated, and their cost will be
estimated. How this happens in detail depends on how the planner is
composed. Attean comes with two roles that implement different
planners, \pmodule{Attean::API::SimpleCostPlanner} will compute all
possible plans and then estimate the cost of all plans, and finally
return the best 5. \pmodule{Attean::API::IDPJoinPlanner}
implements an Iterative Dynamic Programming planner
\cite{Kossmann:2000:IDP:352958.352982}, which prunes plans
aggressively based on their estimated cost in each iteration of query
plan generation. When a final plan tree has been found, the query may
be executed.

>>>>

As can be imagined from the fact that a BGP with just to triple
patterns result in 4 plan trees, a naive query planner may generate a
large number of plans for complex queries. In addition, the proposed
system will generate even more plans, since it considers three sources
of the same data, the cache, the remote endpoint and an LDF
server. Various methods have been developed in the literature to limit
the growth of plans. In addition to a naive planner, we also have an
Iterative Dynamic Programming planner
\cite{Kossmann:2000:IDP:352958.352982}, which prunes plans
aggressively based on their estimated cost in each iteration of query
plan generation.

@@

Based on the algebra tree and plans generated by the models or the
default query planner, as well as the access plans, several
alternative plans will be generated, and their cost will be
estimated. How this happens in detail depends on how the planner is
composed. Attean comes with two roles that implement different
planners, \pmodule{Attean::API::SimpleCostPlanner} will compute all
possible plans and then estimate the cost of all plans, and finally
return the best 5. \pmodule{Attean::API::IDPJoinPlanner} implements an
Iterative Dynamic Programming planner
\cite{Kossmann:2000:IDP:352958.352982}. When a final plan tree has
been found, the query may be executed.
